% ============================================================
\section{Model Validation}
\label{ch:validation}
% ============================================================


% ------------------------------------------------------------
\subsection{Mesh Convergence Study}
\label{sec:mesh-convergence}
% ------------------------------------------------------------

A mesh convergence study was performed to verify that all results are independent of mesh resolution. The study was carried out using a stationary Electric Currents and Heat Transfer solve under the Sim~6 Scenario~1 conditions (mild winter: $T_\text{amb} = \SI{2}{\celsius}$, $h_\text{ext} = \SI{15}{\watt\per\metre\squared\per\kelvin}$), with the final design (Pd--Ag alloy, 20~traces, Chebyshev $p = 1.3$, $V_\text{in} = \SI{12}{\volt}$). Four physics-controlled mesh levels were tested, from Extra Coarse to Extra Fine.

\begin{table}[H]
    \centering
    \caption{Mesh convergence results (stationary EC + HT, Pd--Ag alloy, 20~traces, Chebyshev $p = 1.3$, $V_\text{in} = \SI{12}{\volt}$, Scenario~1 conditions).}
    \label{tab:mesh-convergence}
    \begin{tabular}{@{}lccc@{}}
        \toprule
        \textbf{Mesh level} & \textbf{Domain elements} & $T_\text{min}$ \textbf{(K)} & $\Delta T_\text{min}$ \textbf{vs Extra Fine} \\
        \midrule
        Extra Coarse & 185,852  & 281.607 & 0.004\,K \\
        Coarse       & 241,089  & 281.609 & 0.002\,K \\
        Fine         & 274,402  & 281.611 & $<$0.001\,K \\
        Extra Fine   & 319,050  & 281.611 & --- \\
        \bottomrule
    \end{tabular}
\end{table}

The minimum surface temperature varies by only \SI{0.004}{\kelvin} across all four mesh levels, confirming that the solution is fully converged even at Extra Coarse resolution for this geometry. The Fine mesh (274,402 elements) is selected for all simulations as it matches the Extra Fine result to within \SI{0.001}{\kelvin} while keeping solve times practical.

It should be noted that mesh resolution is more critical for configurations where the result falls close to a threshold. For the Nichrome~V material near the dew point:
\begin{itemize}
    \item \textbf{Nichrome~V, 18~traces, \SI{12}{\volt}:} A coarse mesh predicted a defrost time of 48~minutes, while the Fine mesh reveals that the steady-state $T_\text{min} = \SI{283.09}{\kelvin}$ remains \emph{below} the dew point --- the window never fully defrosts.
    \item \textbf{Nichrome~V, 16~traces, \SI{14.5}{\volt}:} The coarse mesh predicted ``Never'', while the Fine mesh gives 59~minutes ($T_\text{min} = \SI{283.152}{\kelvin}$, barely above the dew point).
\end{itemize}

These borderline cases confirm that the Fine mesh is necessary for reliable results near the dew point threshold, and justify its use throughout this study.


% ------------------------------------------------------------
\subsection{Comparison to Literature}
\label{sec:literature-validation}
% ------------------------------------------------------------

The model physics and boundary condition values are validated against published experimental and numerical studies.

The convection coefficients used in this model ($h_\text{ext} = \SI{15}{\watt\per\metre\squared\per\kelvin}$, $h_\text{int} = \SI{7}{\watt\per\metre\squared\per\kelvin}$) are compared with experimental measurements by Ho\.{z}ejowska et al.\ \cite{hozejowska2019}, who reported measured $h$~values for automotive glass under various driving conditions. Their results support the order of magnitude used in this study, with exterior values in the range \SIrange{10}{25}{\watt\per\metre\squared\per\kelvin} depending on vehicle speed.

R\"uhl et al.\ \cite{ruhl2016} performed coupled finite element simulations of electrically heated glass panes with resistive lines, validated against infrared thermography and thermocouple measurements. Their modelling approach --- coupling electric currents with heat transfer via Joule heating in a 2D representation --- is directly analogous to the physics setup used in this work.

Koshlak et al.\ \cite{koshlak2024} measured that 83--85\% of the heat generated in electrically heated automotive glass is directed inward (toward the cabin side), which is consistent with the asymmetric convection coefficients used in this model ($h_\text{int} < h_\text{ext}$, meaning less heat loss to the interior).

% ------------------------------------------------------------
\subsection{Back-of-Envelope Power and Temperature Estimate}
\label{sec:back-of-envelope}
% ------------------------------------------------------------

An independent analytical estimate of the steady-state average temperature provide a direct check on the numerical results. In this section I used the recommended design from the previous simulations, which is Pd--Ag alloy with 20~traces at \SI{12}{\volt}, because this was the final design that got selected. The final Chebyshev spacing changes where the heat is more concentrated, it does not change the total electrical power input, so the same average-temperature estimate can still be used for the final 20-trace design also.

Each trace has electrical resistance:
\begin{equation}
    R_\text{trace} = \frac{L_\text{glass}}{\sigma_\text{trace} \cdot w_\text{trace} \cdot t_\text{trace}}
    \label{eq:trace-resistance}
\end{equation}
For the selected Pd--Ag design ($\sigma = \SI{2.3e6}{\siemens\per\metre}$):
\begin{equation}
    R_\text{trace} = \frac{1.5}{2.3 \times 10^6 \times 1.7 \times 10^{-3} \times 0.11 \times 10^{-3}} = \SI{3.49}{\ohm}
\end{equation}
The power per trace is $P_\text{trace} = V_\text{in}^2 / R_\text{trace} = 144 / 3.49 = \SI{41.3}{\watt}$, and the total power for 20~traces is:
\begin{equation}
    P_\text{total} = 20 \times 41.3 = \SI{825.8}{\watt}
\end{equation}

Note that this physical power is correctly reproduced in the 2D COMSOL model through the $\sigma_\text{eff}$ correction (\Cref{eq:sigma-eff}): the effective resistance in the model is $R_\text{model} = L_\text{glass}/(\sigma_\text{eff} \cdot w_\text{trace} \cdot t_\text{glass}) = L_\text{glass}/(\sigma_\text{trace} \cdot w_\text{trace} \cdot t_\text{trace}) = R_\text{trace}$.

At steady state, the total Joule heating must equal the convective losses from both sides of the glass:
\begin{equation}
    P_\text{total} = (h_\text{ext} + h_\text{int}) \cdot A_\text{glass} \cdot (T_\text{avg} - T_\text{weighted})
    \label{eq:energy-balance}
\end{equation}
where $A_\text{glass} = L_\text{glass} \times H_\text{glass} = \SI{1.2}{\metre\squared}$ and the convection-weighted ambient temperature is:
\begin{equation}
    T_\text{weighted} = \frac{h_\text{ext} \cdot T_\text{amb} + h_\text{int} \cdot T_\text{cabin}}{h_\text{ext} + h_\text{int}} = \frac{15 \times 275.15 + 7 \times 293.15}{22} = \SI{280.9}{\kelvin}
\end{equation}

Solving for $T_\text{avg}$:
\begin{equation}
    T_\text{avg} = T_\text{weighted} + \frac{P_\text{total}}{(h_\text{ext} + h_\text{int}) \cdot A_\text{glass}} = 280.9 + \frac{825.8}{22 \times 1.2} = 280.9 + 31.3 = \SI{312.2}{\kelvin}
\end{equation}

The analytical estimate for the selected 20-trace Pd--Ag design is therefore a steady-state surface-average temperature of approximately \SI{312.2}{\kelvin}. This basically means the system is going toward this temperature in the long-time limit, not that the whole glass suddenly become this value at one exact time during the early transient. This value is intentionally an \emph{average} over the whole glass area, so it is expected to be much higher than the reported minimum temperatures for the same design (for example \SI{288.2}{\kelvin} for the uniform 20-trace case, or \SI{295.0}{\kelvin} for the Chebyshev $p = 1.3$ layout), because those minima happens at the coldest local points near the glass edges and not over the full surface.

The exported COMSOL surface-average data for the final Chebyshev $p = 1.3$ design confirm this estimate pretty good. The average temperature rises from \SI{278.15}{\kelvin} initially to \SI{294.86}{\kelvin} at \SI{6}{\minute}, \SI{303.54}{\kelvin} at \SI{12}{\minute}, and \SI{312.05}{\kelvin} at \SI{60}{\minute}, which already shows the trend in a clear way. Relative to the COMSOL steady-state value, the response reaches approximately 90\% of the total temperature rise by \SI{19}{\minute}, 95\% by \SI{24}{\minute}, and 99\% by \SI{32}{\minute}, so basically most of the average heating is already there before the full 60 minute result. The final COMSOL value of \SI{312.05}{\kelvin} differs from the analytical estimate by only \SI{0.10}{\kelvin} (\SI{0.03}{\percent}), which is a very small error and because of that it shows excellent agreement between both methods.

This close agreement support the conclusion that:
\begin{itemize}
    \item The $\sigma_\text{eff}$ correction correctly maps the 3D trace geometry to the 2D model
    \item The Joule heating and convective boundary conditions are consistently implemented
    \item The total energy balance of the model is accurate
\end{itemize}


% ------------------------------------------------------------
\subsection{Sensitivity Analysis}
\label{sec:sensitivity}
% ------------------------------------------------------------

The parametric sweeps performed in Sim~2 and Sim~2b serve as a de facto sensitivity analysis, showing how the minimum surface temperature responds to changes in the three main design variables.

\begin{table}[H]
    \centering
    \caption{Sensitivity of minimum surface temperature to design parameters (Pd--Ag alloy, baseline: 14~traces, \SI{12}{\volt}).}
    \label{tab:sensitivity}
    \begin{tabular}{@{}lcc@{}}
        \toprule
        \textbf{Parameter change} & $\Delta T_\text{min}$ \textbf{(K)} & \textbf{Sensitivity} \\
        \midrule
        $n_\text{traces}$: 14 $\to$ 16 (+2 traces) & +1.40 & \SI{0.70}{\kelvin}/trace \\
        $V_\text{in}$: 12 $\to$ \SI{14.5}{\volt} (+\SI{2.5}{\volt}) & +1.16 & \SI{0.46}{\kelvin\per\volt} \\
        Material: Pd--Ag $\to$ Nichrome~V & $-1.49$ & --- \\
        \bottomrule
    \end{tabular}
\end{table}

The results confirm that \textbf{the number of traces is the most influential parameter}, followed by applied voltage. The choice of trace material has a strong effect through its conductivity: higher conductivity produces more Joule heating per unit length of trace.

The external heat transfer coefficient $h_\text{ext}$ is also a sensitive parameter (as noted in the literature \cite{hozejowska2019}), since it directly controls the rate of heat loss from the glass. This was systematically addressed in Sim~6 (\Cref{sec:sim6}), which swept $h_\text{ext}$ alongside $T_\text{amb}$ and $T_\text{dew}$ across five realistic weather scenarios, confirming that the final design remains robust across all tested conditions.
